Black-swan events in animal populations

### 2016-07-13 text/ms_pnas.tex
Add nonbreaking space

Given the prevalence of downwards events, we refit our heavy-tailed models to
measure the degree of skewness \(\gamma\) of the process noise using a skew-$t$
distribution (Fig.~4a), and used these models to make near-term risk forecasts.
Aggregated across populations with strong evidence of heavy tails (median \(\nu
< 10\)), 85\% of the \(\gamma\) probability density was below 1, indicating
strong evidence of downwardly skewed process noise (Fig.~4B,
Fig.~S\figskewnu). In contrast, populations that did not have heavy
tails (median \(\nu \geq 70\)) had little evidence of skewed process noise
(Fig.~4B; 90\% of 95\% credible intervals overlapped 1). Projecting these
heavy-tailed populations forward five years revealed that assuming standard
normal process noise underestimated risk (99\% lower credible interval of
abundance) by \crashUnderRange-fold (interquartile range; Fig.~4C,
Fig.~S\figskewprojections).

>>>>

Given the prevalence of downwards events, we refit our heavy-tailed models to
measure the degree of skewness \(\gamma\) of the process noise using a skew-$t$
distribution (Fig.~4a), and used these models to make near-term risk forecasts.
Aggregated across populations with strong evidence of heavy tails (median \(\nu
< 10\)), 85\% of the \(\gamma\) probability density was below 1, indicating
strong evidence of downwardly skewed process noise (Fig.~4B,
Fig.~S\figskewnu). In contrast, populations that did not have heavy
tails (median \(\nu \geq 70\)) had little evidence of skewed process noise
(Fig.~4B; 90\% of 95\% credible intervals overlapped~1). Projecting these
heavy-tailed populations forward five years revealed that assuming standard
normal process noise underestimated risk (99\% lower credible interval of
abundance) by \crashUnderRange-fold (interquartile range; Fig.~4C,
Fig.~S\figskewprojections).
